Adding selection to \stdpopsim: oh how the tables have turned

### 2024-05-23 analysis2_manuscript.tex
intro clean up

\section*{Introduction}
    \label{introduction}
    % natural selection
    Natural selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of natural selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift. The impact of selection on genetic variation
    is often studied using population genetic models, which can be
    used to generate predictions about the patterns of genetic variation

    % simulation
    As the complexity of population genetic datasets has increased,
    simulation has become a critical tool for interpretation, 
    analysis, and exploration of realistic evolutionary models.
    Simulation in population genetics has a long history 
    including both backward in time coalescent simulations
    \citep{kingman1982genealogy,hudson1983testing, hudson1990gene}
    and forward in time simulations of complex demography and selection
    \citep[e.g.,][]{gillespie1984molecular,thornton2014c++, haller2019slim}.
    The development of simulation tools has been driven by the need to
    understand the effects of complex evolutionary processes on genetic
    variation, to provide a null model for hypothesis testing, to
    to explore the power and limitations of statistical methods, and 
    increasingly to provide a basis for machine learning and other
    simulation-based inference methods.

>>>>

\section*{Introduction}
    \label{introduction}
    % natural selection
    Natural selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of natural selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift \cite[e.g.,][]{gillespie1991causes}.
    For instance changes in population size can lead to fluctuations
    in genetic diversity across a recombining chromosome 
    that can mimic the effects of selection \citep{simonsen1995properties, barton1998effect},
    and lead to spurious inferences about the strength and targets of genetic adaptation
    \cite{simonsen1995properties,akey2004population,nielsen2005genomic}.
    In turn selection can confound our ability to infer demographic 
    history from allele frequencies \citep{ewing2016consequences} and
    estimates of inverse coalescent rate \citep{schrider2016effects}.
    Thus it is imperative to joingly account for the effects of selection
    and demography when inferring evolutionary history from genetic data
    however this is a challenging task from a modeling perspective.

    % simulation
    To meet this need the field of population genetics
    has turned to simulation.
    Simulation has become a critical tool for interpretation, 
    analysis, and exploration of realistic evolutionary models.
    Simulation in population genetics has a long history 
    including both backward in time coalescent simulations
    \citep{kingman1982genealogy,hudson1983testing, hudson1990gene}
    and forward in time simulations of complex demography and selection
    \citep[e.g.,][]{gillespie1984molecular,thornton2014c++, haller2019slim}.
    The development of simulation tools has been driven by the need to
    understand the effects of complex evolutionary processes on genetic
    variation \citep[e.g.,][]{galloway2020few}, to provide a null model for hypothesis testing
    \citep[e.g.,][]{hudson1992statistical}, to
    to explore the power and limitations of statistical methods \cite[e.g.,]{przeworski2002signature},
    and increasingly to provide a basis for machine learning and other
    simulation-based inference methods \citep[e.g.,]{kern2018diplos}.
    While this is so, joint simulation of complex demography and selection
    is challenging, and requires a deep understanding of the underlying
    evolutionary processes, as well as a number of parameter choices including
    the strength of selection, the distribution of fitness effects, and the
    recombination rate, as well as a parameterized model of demography.
    This is dounting task for many researchers, and can be a barrier to
    the adoption of simulation-based methods in population genetics.
    Further, sharing and comparing simulation results among studies can 
    itself be challenging, as different simulation tools may use different
    models and parameterizations, and may not be directly comparable.
    This is a major limitation for the field, as it can make it difficult
    to assess the robustness of results, and to compare the results of
    different studies.
